---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# rwalkable

The goal of rwalkable is to look up and summarise some information about the walkability of a neighbourhood.  We look at two components of walkability: 

- how many places are there within walking distance that you might want to go to (per hectare)?
- is there a reasonably dense network of roads or paths to walk on (number of road segments connections minus number of intersections, per hectare)

We use data from OpenStreetMap for both components, via the `osmdata` package: it provides both a road network and a list of locations ('amenities') that someone has thought worth adding to the map.  Most of the heavy lifting is done by the `dodgr` package. 

## Example

The location can be specified as a geographic area that OpenStreetMap knows about, or as a two-element vector of latitude and longitude

```{r}
library(rwalkable)
nearby("Paris, France")
nearby("Paris, Texas")
```
