---
title: "Using the rwalkable package"
author: "Stuart Lee, Thomas Lumley, Alan Pearse"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## rwalkable

We have legs for walking. This is a true fact. Walking for long distances can 
be painful. This is also a true fact. This package `rwalkable` eases the pain
by exploring the walkability of neighbourhoods.

We make use of `osmdata` and `dodgr` packages to estimate walkability metrics
such as points of interest per hectare. 

## Finding amenities that are `nearby()`

Walkable neighbourhoods have lots of points of interest (amenities) 
that are within some walkable distance.  

Let's look at points of interest nearby Paris, France and compare them
to Paris, Texas, USA
```{r}
library(rwalkable)
paris <- nearby("3rd Arrondissement, Paris, France")
paris

the_other_paris <- nearby("Paris, Texas, USA")
the_other_paris
```

The location can also defined by a vector of longitidue and latitude 
representing the centre of a neighbourhood.

By default, we consider an distance walkable if it's within 800m radius
of the location. 

We can modify this with the radius argument, which takes
a walking distance in metres,

```{r, eval = FALSE}
nearby("Paris, France", radius = 2000)
```

or we can estimate all points of interest for a given walking time in minutes

```{r, eval = FALSE}
nearby("Paris, France", radius = walk_time(15))
```

By default all amenities are to be points of interest, this can modified
with the amenities argument. Valid amenities can be found on 
[OpenStreetMap](https://wiki.openstreetmap.org/wiki/Key:amenity)

```{r, eval = FALSE}
nearby("Paris, France", amenities = "cafe")
```

We can also make an interactive map of the neighbourhood with the 
amenities using leaflet. There's a dropdown menu on the top right hand 
side of the map to filter amenties that are not interesting out.

Here's a walkable neighbourhood
```{r}
plot(paris, overlay_isochrone = FALSE)
```

And a not so walkable neighbourhood

```{r}
plot(the_other_paris, overlay_isochrone = FALSE)
```
